Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-16 analysis/paper/paper.Rmd
wordsmithing

We fitted Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000 and thinning of 1) using the `cumulative(link = "probit")` family function for ordinal scale data using using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
Priors were selected to be weakly informative and deemed suitable through using `pp_check()` to examine the predictions based on priors only (using the parameter `sample_prior = only` in `brm()`).
Priors over all parameters were set as: normal (mean = 0.00, SD = 1.0) distributions for both fixed parameters and random intercepts.

>>>>

We fitted Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000 and thinning of 1) using the `cumulative(link = "probit")` family function for ordinal data using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
Priors were selected to be weakly informative and deemed suitable through using `pp_check()` to examine the predictions based on priors only (using the parameter `sample_prior = only` in `brm()`).
Priors over all parameters were set as: normal (mean = 0.00, SD = 1.0) distributions for both fixed parameters and random intercepts.
